---
title       : LOOPdata
subtitle    : Commercial Nuclear Power Experiences
author      : Farkas
job         : praEngineer
logo        : logo_small.jpg
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

1. Risk exposure
2. NRC event data
3. EIA event data

--- .class #id 

## Exposure

<h4>Total hours of exposure in one year at all 72 sites </h4>
```{r, echo=FALSE}
72*24*365

```

--- .class #id 

## NRC Event Logs

Plant operators keep the NRC informed on a defined set of problems via phone calls log as <a href="http://www.nrc.gov/reading-rm/doc-collections/event-status/event/">events</a>.

More complex events are described via <a href="https://lersearch.inl.gov/LERSearchCriteria.aspx">reports</a>.  Some of these describe "loss of offsite power"" events.

--- .class #id 

## EIA Appendix B Logs 

<h3>Form OE-417 logs</h3>

<a href="http://www.eia.gov/electricity/monthly/">Major Disturbances and Unusual Occurrences</a>, particularly Table B.1

```{r table,results='asis',comment=NA,echo=FALSE}
load("2014OE417s.rda")
df417s <- data.frame(OE417s)
library(xtable)
options(xtable.type='html')
xtable(head(subset(df417s,select=c(Event.Date.and.Time,Utility.Power.Pool,NERC.Region,Type.of.Disturbance))))


```

--- .class #id 

## Anticipating LOOP

A statistical method shows how the likelihood of a grid-induced LOOP is a strong function of the location of the plant (i.e., regional dependence) as well as the season of the year (i.e., seasonal dependence).  To establish a statistically meaningful data set, grid-centered LOOP events were enriched by merging traditional LOOP events (NRC) with events hypothesized to be pre-cursors to LOOP events (EIA).  The duration of grid-centered LOOPs (directly related to the LOOP-non-recovery probability) averaged from three to nine hours.  The effect on the non-recovery probability as a result of this unexpectedly long duration is left to a future report.

